---
title: "Data_manipulation"
author: "Shan Jiang, Jieqi Tu"
date: "12/7/2018"
output: github_document
---
```{r message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
```

```{r message=FALSE, warning=FALSE}
# Import data
cancer_raw = readr::read_csv("./Data/Cancer_Registry.csv") %>% 
  janitor::clean_names() 

dim(cancer_raw)
head(cancer_raw)

# Check NA values for each column
n_NA = sapply(cancer_raw[1:34], function(x) sum(length(which(is.na(x)))))
n_NA

# Check the percentage of NA values for each column
percentage_NA = sapply(cancer_raw[1:34], function(x) sum(length(which(is.na(x)))) / 3047)
percentage_NA
```

There are in total `r ncol(cancer_raw)` variables  and `r nrow(cancer_raw)`observations in the dataset. 

* The outcome variable in this datset is `target_death rate`(Continuous VARIABLE);

* There are remaining `r ncol(cancer_raw)-1` predictors avaliable for use.

### Here are descriptive statistics for `target_death rate`

we first need to look at the distributions of our outcome variable.

```{r}
cancer_raw %>% 
  ggplot(aes(x = target_death_rate)) + 
    geom_histogram(aes(y = ..density..),  
                   binwidth = 2, colour = "black", fill = "white") +
    geom_density(alpha = .1, fill = "#FF6666") +
    geom_vline(aes(xintercept = mean(target_death_rate, na.rm = T)),   # Ignore NA values for mean
               color = "red", linetype = "dashed", size = 1)# Overlay with transparent density plot
```

### Data cleaning
```{r creating subsets for type(a) and type(b) variables}
# Discard columns that have more than 10% NA values 
cancer_raw = 
  cancer_raw %>% 
  select(-pct_private_coverage, -pct_some_col18_24)

# Create a new dataset for type (a) variables
cancer_a_raw = 
  cancer_raw %>% 
  select(target_death_rate, avg_ann_count, avg_deaths_per_year, incidence_rate, study_per_cap)

# Create a new dataset for type (b) variables
cancer_b_raw = 
  cancer_raw %>% 
  select(-target_death_rate, -avg_ann_count, -avg_deaths_per_year, -incidence_rate, -study_per_cap)
```

```{r data cleaning}
cancer_b_raw =
  cancer_b_raw %>% 
  # select median age as the only predictor to reflect the population age level
  select(-median_age_male, -median_age_female) %>% 
  # select median income as the only predictor to relect the population income level
  select(-binned_inc) %>% 
  # select percentage of residents employed as the only predictor to relect the population employment level
  select(-pct_unemployed16_over) %>% 
  # select percent of county residents with private health coverage as the only predictor to relect the population health coverage level
  select(-pct_private_coverage_alone) %>% 
  # select percentage of whits as the only predictor to relect the race proportion
  select(-pct_black, -pct_asian)
```

### Here are descriptive statistics for predictors



```{r}

```


### Variable selection 

We are only interested in working with a subset of the most relevant variables.

* For combination of *race*:we combined the `pct_white`, `pct_black`, `pct_asian`, `pct_other_race`. 


```{r}
## categorical variable 


##
```

## Multiple Linear Regression
