---
title: "Data_manipulation"
author: "Shan Jiang"
date: "12/7/2018"
output: github_document
---
```{r message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
```

```{r message=FALSE, warning=FALSE}
cancer_raw = readr::read_csv("./Data/Cancer_Registry.csv") %>% 
  janitor::clean_names() 

head(cancer_raw)

```

There are in total `r ncol(cancer_raw)` variables  and `r nrow(cancer_raw)`observations in the dataset. 

* The outcome variable in this datset is `target_death rate`(Continuous VARIABLE);

* There are remaining `r ncol(cancer_raw)-1` predictors avaliable for use.

### Here are descriptive statistics for `target_death rate`

we first need to look at the distributions of our outcome variable.

```{r}
cancer_raw %>% 
  ggplot(aes(x = target_death_rate)) + 
    geom_histogram(aes(y = ..density..),  
                   binwidth = 2, colour = "black", fill="white") +
    geom_density(alpha = .1, fill = "#FF6666") +
    geom_vline(aes(xintercept = mean(target_death_rate, na.rm = T)),   # Ignore NA values for mean
               color = "red", linetype = "dashed", size = 1)# Overlay with transparent density plot
```

### Here are descriptive statistics for predictors



```{r}

```


### Variable selection 

We are only interested in working with a subset of the most relevant variables.

* For combination of *race*:we combined the `pct_white`, `pct_black`, `pct_asian`, `pct_other_race`. 


```{r}
## categorical variable 


##
```

## Multiple Linear Regression
